Determinants of Financial Well-Being: The Role of Demographics, Psychosocial Factors, and Financial Literacy

### 2024-12-04 paper/paper.qmd
Updated sketches and added explanation
of variable selection in the paper.

>>>>

Note that this study employs categorical grouping for variables that could be continuous (such as age and income). This approach offers several advantages in survey research: it improves interpretability of results across demographic groups, facilitates statistical comparisons between meaningful socioeconomic segments, and aligns with typical policy and program planning categories. For sensitive variables like income and age, categorical grouping also helps protect respondent privacy while maintaining sufficient detail for analysis. Additionally, the use of standardized categories (in age, education, and income) enables easier comparison with other survey research and demographic studies.
